---
  title: "Untitled"
  output: html_document
---
  
  
  
  
### Question 1:
  
Using a loop, print the integers from 1 to 50. 
```{r, eval = FALSE}
for (i in 1:50) print(i)

```

### Question 2:

A.  Using a loop, add all the integers between 0 and 1000.
```{r}
sum = 0
for (i in 0:1000) {
  sum = sum + i
}
```

B. Now, add all the EVEN integers between 0 and 1000 (hint: use seq())
```{r}
even_sum = 0
for (i in seq(0,1000, by =2)) {
  even_sum = even_sum + i
}
```

C. Now, repeat A and B WITHOUT using a loop.
```{r}
#A
a_vals <- 0:1000
sum(a_vals)
#B
b_vals <- seq(0,1000, by=2)
sum(b_vals)
```


### Question 3:

Here is a dataframe of survey data containing 5 questions :
  
```{r}
survey <- data.frame(
  "participant" = c(1, 2, 3, 4, 5, 6),
  "q1" = c(5, 3, 2, 7, 11, 0),
  "q2" = c(4, 2, 2, 5, -10, 99),
  "q3" = c(-4, -3, 4, 2, 9, 10),
  "q4" = c(-30, 5, 2, 23, 4, 2),
  "q5" = c(88, 4, -20, 2, 4, 2)
)
```
The response to each question should be an integer between 1 and 5. Obviously, we have some bad values in the dataframe. The goal of this problem is to fix them.

A. Using a loop, create a new dataframe called survey.clean where all the invalid values (those that are not integers between 1 and 5) are set to NA.
```{r}
survey.clean <- survey
for(i in 1:dim(survey)[1]) {
  for(j in 2:dim(survey)[2]){
    if (!(survey[i,j] %in% 1:5)) {
      survey.clean[i,j] <- NA
    } else {
      survey.clean[i,j] <- survey[i,j]
    }
  }
}

survey.clean2 <- survey
for(i in 2:dim(survey.clean2)[2]) {
  survey.clean2[,i] <- ifelse(survey.clean2[,i] %in% 1:5, survey.clean2[,i], NA)
}

```

B. Now, again using a loop, add a new column to the dataframe called “invalid.answers” that indicates, for each participant, how many bad answers they gave.
```{r}
for(i in 1:dim(survey.clean)[1]) {
  survey.clean$invalid.answers[i] <- sum(is.na(survey.clean[i,2:6]))
}
```

